IJAR Bayesian Nonparametrics Special Issue Manuscript

### 2015-10-21 ijar-npb-ms.tex
ref to risk analysis paper in intro

@@

***publish code in Louis' \textbf{R} spackage \texttt{ReliabilityTheory}
(which contains the function to calculate the survival signature)***

@@

***Some extra illustrations? E.g. the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper?
(could nicely illustrate decision making with intervals:
do I prefer adding redundancy such that there is a chance for a large effect, but high uncertainty for it,
or do I rather add redundancy such that effect is smaller but more certain?***

***Other interesting extra illustration:
show effect of replacement of components in a system at certain time points
(failed component or preventive replacement),
replaced components constitute a new type with shifted component reliability function***

>>>>

This paper implements the nonparametric approach described in Section~4 of ***Risk Analysis paper***
and extends it to sets of priors.

@@

***publish code in Louis' \textbf{R} package \texttt{ReliabilityTheory}
(which contains the function to calculate the survival signature)***

@@

***Some extra illustrations? E.g. the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper?
(could nicely illustrate challenges in decision making with intervals:
do I prefer adding redundancy such that there is a chance for a large effect, but high uncertainty for it,
or do I rather add redundancy such that effect is smaller but more certain?***

***Other interesting extra illustration:
show effect of replacement of components in system at certain time points
(could be corrective (component failed) or preventive replacement),
replaced components constitute a new type with shifted component reliability function***
